---
title: "Loan Application Analysis Project"
author: "Nikul Chhabhaiya - 2505101270035"
division: "C"
date: "2026-09-17"
output: html_document
---

## Introduction

This project analyzes the Loan Application database using R.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

## Import Dataset

```{r}
loan <- read.csv("Data.csv")
head(loan)
```

## Dataset Summary

```{r}
summary(loan)
str(loan)
```

## Loan Status Count

```{r}
table(loan$Status..Approved.Rejected.Pending.)
```

## Loan Type Chart

```{r}
ggplot(loan, aes(x = Loan.Type)) +
  geom_bar(fill = "steelblue") +
  labs(title = "Loan Types", x = "Loan Type", y = "Count")
```

## Loan Amount by Loan Type

```{r}
ggplot(loan, aes(x = Loan.Type, y = Loan.Amount)) +
  geom_boxplot(fill = "lightgreen") +
  labs(title = "Loan Amount by Loan Type")
```

## City-wise Applications

```{r}
ggplot(loan, aes(x = City...Branch.Location)) +
  geom_bar(fill = "orange") +
  labs(title = "Applications by City", x = "City", y = "Count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Loan Status Pie Chart

```{r}
status <- table(loan$Status..Approved.Rejected.Pending.)

pie(status,
    col = rainbow(length(status)),
    main = "Loan Status Distribution")
```

## Interest Rate Distribution

```{r}
ggplot(loan, aes(x = Interest.Rate....)) +
  geom_histogram(bins = 10, fill = "red", color = "black") +
  labs(title = "Interest Rate Distribution",
       x = "Interest Rate (%)",
       y = "Count")
```

## Conclusion

The project imports the dataset successfully and analyzes loan applications by status, loan type, loan amount, and city.